cardinalR: Generating interesting high-dimensional data structures

### 2025-10-05 paper-cardinalR.Rmd
Updated table 10

```{r noise-tb-pdf, eval=knitr::is_latex_output()}
noise_fun_tb |> 
  kable(caption = "cardinalR noise dimensions generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, table.pos = "H")  |>
  column_spec(1, width = "3cm") |>
  column_spec(2, width = "9cm")
```

>>>>

```{r noise-tb-pdf, eval=knitr::is_latex_output()}
noise_fun_tb |> 
  kable(caption = "cardinalR noise dimensions generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, table.pos = "H")  |>
  column_spec(1, width = "2.5cm") |>
  column_spec(2, width = "10.5cm")
```
